\documentclass[11pt,a4paper]{article}

% ---------------------------------------------------------------------------
% EDGAR.jl — User Manual
% Compile with: pdflatex EDGAR.tex  (run twice for the table of contents /
% cross-references). No --shell-escape required (uses `listings`, not minted).
% ---------------------------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[colorlinks=true,linkcolor=BlueViolet,urlcolor=BlueViolet,
            citecolor=BlueViolet]{hyperref}
\usepackage[dvipsnames]{xcolor}

% ---- Julia code listing style ---------------------------------------------
\definecolor{codebg}{rgb}{0.97,0.97,0.98}
\definecolor{codekw}{rgb}{0.55,0.10,0.55}
\definecolor{codestr}{rgb}{0.10,0.45,0.20}
\definecolor{codecom}{rgb}{0.45,0.45,0.45}
\definecolor{coderule}{rgb}{0.85,0.85,0.88}
\definecolor{juliaprompt}{rgb}{0.10,0.40,0.80}   % bold blue REPL prompt (distinct from string-green)

\lstdefinelanguage{Julia}{
  morekeywords={function,end,using,import,module,for,in,if,else,elseif,while,
    return,begin,struct,mutable,const,true,false,nothing,do,let,global,local},
  sensitive=true,
  morecomment=[l]{\#},
  morestring=[b]",
}

\lstdefinestyle{julia}{
  language=Julia,
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\small,
  keywordstyle=\color{codekw}\bfseries,
  stringstyle=\color{codestr},
  commentstyle=\color{codecom}\itshape,
  frame=single,
  rulecolor=\color{coderule},
  framesep=6pt,
  xleftmargin=10pt,
  xrightmargin=4pt,
  breaklines=true,
  showstringspaces=false,
  columns=fullflexible,
  keepspaces=true,
  % colour the REPL prompt green to match a real Julia session
  % colour the REPL prompt blue (bold) to stand apart from the green strings
  literate={julia>}{{\textcolor{juliaprompt}{\textbf{julia>}}}}{6},
}
\lstset{style=julia}

% inline code shortcut
\newcommand{\code}[1]{\texttt{\small #1}}

% function signature block: a blank line of vertical space above and below
\newcommand{\sig}[1]{\medskip\noindent\code{#1}\par\medskip}

\titleformat{\section}{\Large\bfseries\color{BlueViolet}}{\thesection}{0.6em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{0.6em}{}

% Tighten itemize: noitemsep zeroes both itemsep and parsep (itemsep alone leaves
% parsep, so items still look spread out); keep a small gap around the whole list.
\setlist[itemize]{noitemsep, topsep=2pt}

% ---------------------------------------------------------------------------
\title{\textbf{EDGAR.jl}\\[0.3em]
       \large A Julia interface to the U.S.\ SEC EDGAR system}
\author{}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
\textbf{EDGAR.jl} pulls company data from the U.S.\ Securities and Exchange
Commission's \href{https://www.sec.gov/search-filings/edgar-application-programming-interfaces}{EDGAR}
system into Julia: a filer's \emph{submission history}, the \emph{XBRL financial
facts} extracted from its filings, cross-filer \emph{frames}, and \emph{full-text
search} of filing contents. It talks to the public
\code{data.sec.gov} / \code{efts.sec.gov} / \code{sec.gov} endpoints with
\code{HTTP.jl} and \code{JSON3.jl}, parses HTML with \code{Gumbo.jl} and
\code{Cascadia.jl}, and caches responses so an interactive session does not
re-download the same data. No API key is required --- only a descriptive
\code{User-Agent} (see \S\ref{sec:ua}).
\end{abstract}

\tableofcontents
\vspace{1em}

% ===========================================================================
\section{Introduction}
\label{sec:intro}

EDGAR (\emph{Electronic Data Gathering, Analysis, and Retrieval}) is the SEC's
filing system. Every public company in the United States files its disclosures
there, and since 2009 the financial statements in those filings are tagged in
\textbf{XBRL}, which is what makes them machine-readable. The SEC publishes this
data through open JSON REST APIs that require no registration and no key.

EDGAR.jl wraps those endpoints behind a small, typed API and stops at plain Julia
values (\code{JSON3} objects and \code{NamedTuple}s), which you can pipe into
\code{Tables.jl}, \code{TimeSeries.jl}, or a database. It covers three kinds of
task:

\begin{itemize}[nosep]
  \item \textbf{Filings} --- list a filer's submissions, download a filing's
        documents, convert them to text, and extract sections such as
        \emph{Financial Statements} and \emph{Management's Discussion}.
  \item \textbf{XBRL financial data} --- a filer's full set of reported facts
        (\code{company\_facts}), one concept over time (\code{company\_concept}),
        or one concept across every filer for a period (\code{xbrl\_frames}).
  \item \textbf{Full-text search} --- search the contents of filings since 2001
        (\code{full\_text\_search}).
\end{itemize}

\noindent
The SEC asks for \textbf{fair use}: at most ten requests per second. EDGAR.jl's
cache (\S\ref{sec:caching}) helps you stay well under that.

% ===========================================================================
\section{Installation}
\label{sec:install}

EDGAR.jl requires \textbf{Julia 1.12 or later}. It is not yet registered, so
install it straight from GitHub:

\begin{lstlisting}
using Pkg
Pkg.add(url = "https://github.com/Trumpingtons/EDGAR.jl")
\end{lstlisting}

\subsection{Setting a User-Agent}
\label{sec:ua}

The SEC's fair-access policy requires every request to identify you with a
\code{User-Agent} header containing your \textbf{name and a contact email}.
\textbf{Without it the SEC returns HTTP 403.} There is no key and no
registration --- just be honest about who is calling. Set yours once with a
single \code{"name email"} string:

\begin{lstlisting}
using EDGAR
set_user_agent("Jane Doe jane@example.com")
\end{lstlisting}

\noindent
\code{set\_user\_agent} validates the string (non-empty, contains an email) and
returns it. If you forget, EDGAR.jl stops with a clear error \emph{before} ever
contacting the SEC.

\subsection{Per Session User-Agent vs. Persistent}
\code{set\_user\_agent} (and \code{set\_config}) set the User-Agent only for the
\emph{current} Julia process --- a new REPL or notebook kernel starts without
one. The resolution order EDGAR.jl uses is:

\begin{enumerate}[nosep]
  \item an explicit value from \code{set\_user\_agent} / \code{set\_config}; else
  \item the \code{SEC\_USER\_AGENT} environment variable; else
  \item an error.
\end{enumerate}

\noindent
So to avoid setting it every session, define the environment variable once.
\code{persist\_user\_agent} writes it into your Julia startup file for you, which
every future Julia process (REPL, script, \emph{and} notebook kernel) reads:

\begin{lstlisting}
persist_user_agent("Jane Doe jane@example.com")  # writes ~/.julia/config/startup.jl
# unpersist_user_agent()                          # removes it again
\end{lstlisting}

\noindent
Equivalently, set \code{ENV["SEC\_USER\_AGENT"] = "Jane Doe jane@example.com"} in
\code{\textasciitilde/.julia/config/startup.jl} (or export it from your shell)
yourself. The User-Agent is \emph{not} a secret --- it is exactly the information
you are transmitting to the SEC --- so storing it in a startup file is fine.

% ===========================================================================
\section{Quick Start}
\label{sec:quickstart}

\subsection{Searching}
\label{sec:qs-search}

Resolve a ticker to a CIK, then search the text of filings:

\begin{lstlisting}
using EDGAR
set_user_agent("Jane Doe jane@example.com")

# Ticker -> 10-digit, zero-padded CIK (exact match -> 0 or 1 row)
id = only(cik("AAPL"; by = :ticker)).cik   # "0000320193"

# Full-text search across filing contents (2001 onward), restricted to 10-K forms
rows = filings_by_text("climate risk"; forms = "10-K")   # a Tables.jl row table
for f in first(rows, 5)
    println(f.filed, "  ", f.form, "  ", f.entity)
end
\end{lstlisting}

\subsection{Financial Data}
\label{sec:qs-findata}

The three XBRL endpoints share the \code{us-gaap} vocabulary and return JSON:

\begin{lstlisting}
# Every XBRL fact a company has reported, in one document
facts = company_facts("320193")
gaap  = facts.facts[Symbol("us-gaap")]      # us-gaap has a hyphen: index by Symbol

# One concept over time (net income, grouped by unit)
ni = company_concept("320193", "us-gaap", "NetIncomeLoss")
println(ni.units.USD[end].val)

# The same concept across every filer for one period (a cross-section)
assets = xbrl_frames("us-gaap", "Assets", "USD", "CY2022Q4I")
println(length(assets.data), " filers reported Assets")
\end{lstlisting}

\noindent
A trailing \code{I} on the frame period (\code{"CY2022Q4I"}) denotes an
\emph{instant} (a balance-sheet point in time); drop it for a \emph{duration}
(a flow such as revenue). See the Glossary (\S\ref{sec:glossary}).

\subsection{Financial Reports}
\label{sec:qs-reports}

\emph{Structured extraction of financial statements from inline XBRL (iXBRL) is
planned and not yet available.} The SEC tags the financial statements directly
inside each filing's primary HTML document; a future release will parse those
\code{<ix:\dots>} tags into tidy tables.

In the meantime you can already work with the filing \emph{documents}: list a
filer's filings, download a filing, convert it to text, and pull named sections
(see \S\ref{sec:api-filings}). For the \emph{tagged numbers} that underlie the
statements today, use the XBRL data API above (\S\ref{sec:qs-findata}) --- the
SEC has already extracted those facts for you, so you rarely need to parse the
iXBRL by hand.


\section{Forms and Entities}


For most corporate analysis, the “big three” report forms (10-K, 10-Q, and 8-K) provide the majority of the useful information. However, several other SEC forms can be extremely valuable depending on what we are researching.

\medskip
\noindent To retrieve any form in EDGAR.jl, pass its \textbf{EDGAR form code} to
\code{forms} in \code{filings\_by\_text} or \code{filings\_by\_cik}; the code is the
name used in each heading below, except where noted (e.g.\ \code{"SC 13D"},
\code{"13F-HR"}, \code{"NPORT-P"}, \code{"N-MFP2"}). For example:

\begin{lstlisting}
filings_by_cik(320193; forms = "8-K")                 # Apple's 8-Ks
full_text_search("climate"; forms = ["10-K", "10-Q"]) # either annual or quarterly
\end{lstlisting}

\subsection{“Big Three” Report Forms}

\subsubsection{10-K: Annual Report}
The annual report, denoted 10-K, provides a comprehensive overview of a company's business and financial performance for the fiscal year.

\subsubsection{10-Q: Quarterly Report}
			
The quarterly report, denoted 10-Q, updates investors on the company's performance during a fiscal quarter. There is typically no Q4 10-Q because the annual 10-K covers the full year. Unlike a 10-K, the financial statements are usually reviewed but not fully audited.

\subsubsection{8-K: Current Report}

The current report, denoted 8-K, is filed whenever a material event occurs that investors should know about. Unlike 10-K and 10-Q filings, 8-K filings are event-driven and can be filed at any time. Common triggers include:
\begin{itemize}
  \item Acquisitions or mergers
  \item Bankruptcy
  \item CEO or CFO changes
  \item Director appointments or resignations
  \item Major contracts
  \item Earnings announcements
  \item Changes in auditors
  \item Delisting notices
\end{itemize}


\subsection{Foreign Companies}

\subsubsection{20-F: Annual Report}
The foreign-issuer equivalent of Form 10-K. Filed annually by foreign companies whose securities are traded in U.S. markets. Useful for understanding a foreign company’s business, risks, financial condition, and corporate governance. Examples include Toyota Motor Corporation and SAP SE.

\subsection{Corporate Governance}
\subsubsection{Proxy Statement (DEF 14A)}
Many researchers consider the Proxy Statement (DEF 14A)\footnote{\textbf{DEF} denotes Definitive and \textbf{14A} refers to proxy materials filed under Section 14(a) of the Securities Exchange Act.} the best source of information on executive compensation, directors, and corporate governance. Typical contents include:
\begin{itemize}
\item Executive compensation
\item Director biographies
\item Board composition
\item Related-party transactions
\item Shareholder proposals
\end{itemize}


\subsection{Tender Offers and Mergers}
\subsubsection{Schedule TO}
Tender offer filing used in acquisitions, buyouts, and going-private transactions. Useful for understanding the terms, financing, and parties involved in a tender offer.
\begin{itemize}
\item Acquisitions
\item Buyouts
\item Going-private transactions
\end{itemize}



\subsection{Securities Offerings}

\subsubsection{Form S-1}
Form S-1 is the registration statement typically used by companies seeking to go public through an initial public offering (IPO). It is useful for understanding a company before its IPO. Typical contents include:
\begin{itemize}
  \item Detailed business description
  \item Risk factors
  \item Use of proceeds
  \item Management team
  \item Industry overview
\end{itemize}

\subsubsection{Form S-3}
Form S-3 is a simplified registration statement used by eligible seasoned issuers to register additional securities offerings. It is commonly used for follow-on offerings and shelf registrations.


\subsection{Ownership and Insider Activity}

\subsubsection{Schedule 13D}
Filed when an investor acquires more than 5\% of a company's shares and intends to influence management or corporate policies. Useful for identifying activist investors, takeover attempts, and significant ownership positions.

\subsubsection{Schedule 13G}
A simplified alternative to Schedule 13D for passive investors who acquire more than 5\% of a company's shares without seeking to influence management or control of the company.

\subsubsection{Form 4}
Reports purchases and sales of company securities by directors, officers, and beneficial owners holding more than 10\% of the company's shares. Useful for tracking insider trading activity.

\subsection{Holdings of Institutional Investors}

\subsubsection{Form 13F}
An aggregated portfolio disclosure by an institutional investment manager. It primarily reports the holdings managed by the filing institutional investment manager, rather than a detailed fund-by-fund portfolio breakdown. The EDGAR form code is \code{"13F-HR"} (the holdings report; \code{"13F-NT"} is a notice that another manager reports the holdings).

\subsubsection{Form N-PORT}
Individual registered fund portfolio disclosure, providing monthly portfolio reports required for registered open-end investment companies, including most mutual funds and ETFs \footnote{Main exemptions/exceptions include: (1) money market funds, which are primarily regulated under Form N-MFP instead (\S\ref{N-MFP}); (2) exchange-traded products that are not 1940 Act funds; (3) funds relying on master-feeder or umbrella structures; (4) newly formed or liquidating funds may benefit from transitional relief and reduced or modified reporting, respectively; (5) small fund conditional exemptions (limited scope).}. Each filing corresponds to a single registered investment fund. N-PORT filings are typically made public with a delay (generally $\sim$60 days after month-end), and therefore are not real-time.

The public EDGAR form code is \code{"NPORT-P"}. N-PORT is highly granular compared to Form 13F:
\begin{itemize}
  \item Individual securities are reported
  \item CUSIPs\footnote{A CUSIP (Committee on Uniform Security Identification Procedures) is a unique nine-character code used to identify North American financial securities, such as stocks, bonds, and mutual funds. Functioning much like a serial number, it uniquely identifies a security and facilitates the accurate tracking of investments, trade processing, and settlement by brokerages, banks, and clearing organizations.} are included
  \item Positions are disclosed at the security level\footnote{Certain holdings may receive confidential treatment in limited, regulator-approved cases.}
  \item Valuation per holding is provided
\end{itemize}

\noindent N-PORT filings may also include portfolio-level classifications and summaries, including,
\begin{itemize}
  \item Equity vs fixed income vs derivatives breakdowns
  \item Sector and asset-type classifications
  \item Country and currency exposure summaries
  \item Liquidity categories
\end{itemize}

\noindent N-PORT filings may further include risk and exposure metrics (where applicable), including,
\begin{itemize}
  \item Portfolio duration (for fixed income)
  \item VaR-style risk measures (where applicable)
  \item Concentration levels
  \item Exposure breakdowns across risk factors
\end{itemize}

\subsubsection{Form N-MFP}\label{N-MFP}
Most money market funds are not required to file N-PORT in the same way as other mutual funds. They are primarily regulated under Form N-MFP instead, which is tailored specifically to money market instruments. The current EDGAR form code is \code{"N-MFP2"} (\code{"N-MFP3"} from the 2024 amendments).

\subsection{Entities}

Every filer on EDGAR --- whoever submits a filing --- is an \emph{entity},
identified by a \textbf{CIK} (Central Index Key, \S\ref{sec:glossary}). An entity is
not always an operating company: it may be a registered \emph{investment} company (a
mutual fund, ETF, or money-market fund), an institutional investment manager, or an
individual (e.g.\ a director filing Form 4). The SEC tags each filer with an
\code{entityType}, and which forms it files follows from that type:

\begin{itemize}
  \item \code{"operating"} --- an operating company (or an institutional manager).
    Files the corporate forms above: 10-K / 10-Q / 8-K, DEF 14A, S-1/S-3, 20-F for
    foreign issuers; a manager also files \textbf{13F}.
  \item \code{"investment"} --- a registered investment company: a mutual fund or
    ETF (files \textbf{N-PORT}), or a money-market fund (files \textbf{N-MFP}).
\end{itemize}

\noindent EDGAR.jl exposes entities through three functions. \code{cik} maps a name
or ticker to a CIK, covering entities that \emph{have} a ticker (companies and
listed ETFs/funds). \code{profile(cik)} returns a single filer's row-invariant
record --- its \code{name}, \code{entityType}, SIC industry, fiscal year-end,
tickers, former names, and so on. And the \code{entity} column of
\code{filings\_by\_text} is simply that filer's name. So a typical workflow is:
resolve the CIK (\code{cik}), inspect the filer (\code{profile}), then pull its
filings of the relevant form (\code{filings\_by\_cik}).

\begin{lstlisting}
id = only(cik("AAPL"; by = :ticker)).cik   # "0000320193"
profile(id).entityType                      # "operating"
filings_by_cik(id; forms = "10-K")          # its annual reports
\end{lstlisting}


% ===========================================================================
\section{API}
\label{sec:api}

CIKs are the SEC Central Index Key, zero-padded to 10 digits (Apple $\to$
\code{0000320193}). Any \code{cik} argument accepts an integer or a string, with
or without leading zeros (\code{320193}, \code{"320193"} and \code{"0000320193"}
are equivalent); functions normalize to the 10-digit form. Every data call goes
through the cached, User-Agent-aware request layer (\S\ref{sec:caching}).

\subsection{Searching and Company Lookup}
\label{sec:api-search}

\begin{longtable}{@{}p{0.46\textwidth}p{0.50\textwidth}@{}}
\toprule
\textbf{Function} & \textbf{Purpose} \\
\midrule
\endhead
\code{cik()} & Every company as a row table. \\
\code{cik(entity; by = :name | :ticker | :any)} & The rows matching \code{entity}
  by company name (case-insensitive substring), exact (case-insensitive) ticker, or
  either --- \code{:any} is the default. Same row-table type in every case. \\
\code{full\_text\_search(query; exact, forms, startdate, enddate, from)} &
  Full-text search of filing contents (2001+) via the EDGAR full-text search
  (EFTS) API. Matched as an exact phrase by default (\code{exact = false} for
  loose words); \code{forms} may be a string or a collection; dates are
  \code{"YYYY-MM-DD"}. Returns a row table. \\
\code{filings\_by\_cik(cik; forms, startdate, enddate, from)} &
  A single filer's filings (2001+) via the same EFTS endpoint, using its entity
  filter rather than a text query --- a true "filed by this filer" search.
  Returns a per-filing row table (with XBRL flags and \code{acceptanceDateTime}). \\
\code{profile(cik)} &
  A filer's row-invariant data: name, \code{entityType}, SIC, fiscal year-end,
  tickers, exchanges, former names, etc. \\
\bottomrule
\end{longtable}

\subsubsection{cik}

\sig{cik()}

\sig{cik(entity; by = :name | :ticker | :any)}

\noindent \code{cik()} returns every company; given an \code{entity}, \code{by}
selects how to match it. Always returns a \texttt{Tables.jl} \emph{row table}, a
\texttt{Vector} of \texttt{NamedTuple}s with fields \texttt{company}, \texttt{ticker}
and \texttt{cik} (one record per ticker):

\begin{itemize}[nosep]
  \item \code{:any} (the default) --- rows matching \code{entity} by company name
    (substring) \emph{or} an exact ticker; so a short string like \code{"IBM"}
    finds the ticker and a word like \code{"apple"} finds the name, without saying
    which. Each row is tested once, so a row matching both appears only once.
  \item \code{:name} --- rows whose company name contains \code{entity}
    (case-insensitive substring).
  \item \code{:ticker} --- \code{0} or \code{1} row matching the exact
    (case-insensitive) ticker.
\end{itemize}

\noindent The result type is the same for every form, so it stays type-stable, and
as a plain vector it indexes, filters and feeds straight into any tool that reads
tables, including \texttt{DataFrames}, \texttt{CSV} and \texttt{Parquet} files, or a \texttt{SQLite} database. A
query may yield several rows, because (a) one company can have multiple tickers
(e.g. share classes \code{GOOGL}/\code{GOOG}), and (b) several companies may match
the query in their name.
\begin{lstlisting}
julia> cik("alphabet")           # by = :any (default); "alphabet" matches the name
# Output:
6-element Vector{@NamedTuple{entity::String, ticker::String, cik::String}}:
 (entity = "Alphabet Inc.", ticker = "GOOGL", cik = "0001652044")
 (entity = "Alphabet Inc.", ticker = "GOOG", cik = "0001652044")
 (entity = "Alphabet Inc.", ticker = "GOOGN", cik = "0001652044")
 (entity = "Alphabet Inc.", ticker = "GGLAP", cik = "0001652044")
 (entity = "Alphabet Inc.", ticker = "GOOGM", cik = "0001652044")
 (entity = "Alphabet Inc.", ticker = "GGLBP", cik = "0001652044")

julia> cik("master")
# Output:
5-element Vector{@NamedTuple{entity::String, ticker::String, cik::String}}:
 (entity = "Mastercard Inc", ticker = "MA", cik = "0001141391")
 (entity = "MasterBrand, Inc.", ticker = "MBC", cik = "0001941365")
 (entity = "MasterCraft Boat Holdings, Inc.", ticker = "MCFT", cik = "0001638290")
 (entity = "PUTNAM MASTER INTERMEDIATE INCOME TRUST", ticker = "PIM", cik = "0000830622")
 (entity = "MASTERBEEF GROUP", ticker = "MB", cik = "0002027265")

julia> cik("AAPL"; by = :ticker)
# Output:
1-element Vector{@NamedTuple{entity::String, ticker::String, cik::String}}:
 (entity = "Apple Inc.", ticker = "AAPL", cik = "0000320193")

julia> cik()[1:5]                # first 5 rows
# Output:
5-element Vector{@NamedTuple{entity::String, ticker::String, cik::String}}:
 (entity = "NVIDIA CORP", ticker = "NVDA", cik = "0001045810")
 (entity = "Apple Inc.", ticker = "AAPL", cik = "0000320193")
 (entity = "Alphabet Inc.", ticker = "GOOGL", cik = "0001652044")
 (entity = "MICROSOFT CORP", ticker = "MSFT", cik = "0000789019")
 (entity = "AMAZON COM INC", ticker = "AMZN", cik = "0001018724")
\end{lstlisting}

\subsubsection{filings\_by\_text}

\sig{filings\_by\_text(phrase; exact=true, forms=nothing, startdate=nothing, enddate=nothing, from=0)}

\noindent Also exported as \code{full\_text\_search} --- the SEC's own name for this
endpoint (EFTS) --- and pairs with \code{filings\_by\_cik}. The function
\texttt{filings\_by\_text} discovers \textit{filings} by their content (e.g. "which filings mention 'supply chain disruption'?"). Search the full text of SEC filings, everything filed from 2001 onward, for some \texttt{phrase} through the EDGAR
full-text search (EFTS) API. \code{forms} may be a single string (\code{"10-K"})\footnote{Form 10-K is a detailed \textbf{annual} filing submitted by public companies to the SEC. It provides a comprehensive overview of the company's business activities, financial health, and key risks. The filing includes audited financial statements, management's discussion of financial results, information about the company's operations and strategy, disclosures on legal and regulatory issues, and an assessment of risk factors that could affect future performance.} or a collection; \code{startdate} and \code{enddate}
are \code{"YYYY-MM-DD"} strings; and \code{from} is the 0-based offset used to page
(EFTS returns a fixed page of 100 results per request). By default the
\texttt{phrase} is matched \textbf{exactly} (it is quoted for you), so
\code{"supply chain disruption"} finds only filings with those three words adjacent;
pass \code{exact = false} to match the words loosely instead. Results come back
ranked by relevance, not by date.

It returns a Tables.jl \emph{row table} --- a \texttt{Vector} of
\texttt{NamedTuple}s, one per matching filing, for the current page (up to 100).
There is no total-match count; to page, advance \code{from} in steps of 100 until
you get fewer than 100 rows. The columns are:

\medskip
\noindent
\begin{tabular}{@{}p{0.22\textwidth}p{0.70\textwidth}@{}}
\toprule
\textbf{Column} & \textbf{Meaning} \\
\midrule
\code{cik}        & The filer's 10-digit, zero-padded Central Index Key. \\
\code{entity}     & The filer's name --- a company, mutual fund, ETF, money-market fund, institutional manager, etc. (Tickers are a filer attribute --- use \code{cik}, joining on the CIK; richer filer data is in \code{profile}.) \\
\code{form}       & Form type (e.g.\ \code{10-K}, \code{8-K}). \\
\code{reportDate} & The period the filing covers (may be empty). \\
\code{filed}      & The date the filing was filed. \\
\code{accession}  & The accession number identifying the filing. \\
\code{document}   & The primary document's filename. \\
\code{score}      & Relevance score (higher = better match). \\
\bottomrule
\end{tabular}
\medskip

\begin{lstlisting}
julia> rows = filings_by_text("supply chain disruption"; forms = "10-K", startdate = "2026-01-01");

julia> rows[1]
(cik = "0001622996", entity = "ACRO BIOMEDICAL CO., LTD.", form = "10-K",
 reportDate = "2025-12-31", filed = "2026-02-11",
 accession = "0001640334-26-000241", document = "acbm_10k.htm", score = 13.91)
\end{lstlisting}
\medskip

\noindent Being a Tables.jl source, \code{rows} drops straight into
\code{DataFrame}, \code{CSV} and friends. The submissions-only fields
(\code{acceptanceDateTime} and the XBRL flags) are \emph{not} included here: a text
search spans many filers, so adding them would cost one submissions request per
distinct filer (up to $\sim$100 per page). \code{filings\_by\_cik} adds them cheaply
for a single filer.

\subsubsection{filings\_by\_cik}

\sig{filings\_by\_cik(cik; forms=nothing, startdate=nothing, enddate=nothing, from=0)}

\noindent List a single filer's filings (2001 onward) through the same EFTS
endpoint, but keyed by its \texttt{cik} (an integer or string, padded or not) using
EDGAR's \emph{entity} filter --- the web form's company/CIK field. This is a true
``filed by this filer'' query, unlike full-text searching for the CIK as document
text, which also matches filings that merely \emph{mention} it (e.g.\ a fund listing
the company among its holdings). \code{forms}, the dates and \code{from} behave as
for \code{filings\_by\_text}; it likewise returns a Tables.jl row table, newest-first.

Each row is \textbf{one filing}. There are no filer-level columns (name,
\code{entityType}, SIC, \dots) --- those are invariant for one filer, so they are
not repeated on every row; get them once from \code{profile} (below). The XBRL
flags and \code{acceptanceDateTime} are joined \textbf{per filing} on the accession
(a \code{10-K} is XBRL while a \code{Form 4} is not), and are \code{missing} for any
filing outside the submissions recent window (and \code{isXBRLNumeric} wherever the
SEC reports no value). The columns, in order:

\medskip
\noindent
\begin{tabular}{@{}p{0.24\textwidth}p{0.68\textwidth}@{}}
\toprule
\textbf{Column} & \textbf{Meaning} \\
\midrule
\code{form}               & Form type (e.g.\ \code{10-K}, \code{8-K}). \\
\code{reportDate}         & The period the filing covers (may be empty). \\
\code{filed}              & The date the filing was filed. \\
\code{acceptanceDateTime} & When the SEC accepted the filing (ISO-8601 UTC). \\
\code{accession}          & The accession number identifying the filing. \\
\code{document}           & The primary document's filename. \\
\code{isXBRL}             & Whether the filing carries XBRL data. \\
\code{isInlineXBRL}       & Whether that XBRL is inline (iXBRL). \\
\code{isXBRLNumeric}      & Whether it contains numeric XBRL facts. \\
\bottomrule
\end{tabular}
\medskip

\begin{lstlisting}
julia> rows = filings_by_cik(320193; forms = "8-K", startdate = "2026-01-01");

julia> rows[1]
(form = "8-K", reportDate = "2026-04-30", filed = "2026-04-30",
 acceptanceDateTime = "2026-04-30T20:30:41.000Z",
 accession = "0000320193-26-000011", document = "aapl-20260430.htm",
 isXBRL = true, isInlineXBRL = true, isXBRLNumeric = false)
\end{lstlisting}

\subsubsection{profile}

\sig{profile(cik)}

\noindent A filer's \textbf{row-invariant} data from the SEC submissions document
--- the fields that are the same across all of a filer's filings, returned once
(as a \texttt{NamedTuple}) rather than repeated on every row of
\code{filings\_by\_cik}. \code{cik} may be an integer or string, padded or not. The
fields are:

\medskip
\noindent
\begin{tabular}{@{}p{0.26\textwidth}p{0.66\textwidth}@{}}
\toprule
\textbf{Field} & \textbf{Meaning} \\
\midrule
\code{cik}                  & The filer's 10-digit, zero-padded Central Index Key. \\
\code{name}                 & The filer's name. \\
\code{entityType}           & The filer kind: \code{"operating"} (a company) or \code{"investment"} (a mutual fund / ETF / money-market fund), etc. \\
\code{sic}                  & Standard Industrial Classification code (industry). \\
\code{sicDescription}       & Human-readable industry description. \\
\code{fiscalYearEnd}        & Fiscal year-end as \code{MMDD} (e.g.\ \code{"0926"}). \\
\code{stateOfIncorporation} & State/country of incorporation. \\
\code{tickers}              & Ticker symbols (\texttt{Vector\{String\}}; empty for funds without one). \\
\code{exchanges}            & Exchanges those tickers trade on. \\
\code{ein}                  & Employer Identification Number. \\
\code{category}             & SEC filer category (e.g.\ "Large accelerated filer"). \\
\code{website}              & The filer's website (may be empty). \\
\code{description}          & Free-text description (may be empty). \\
\code{formerNames}          & Prior names (\texttt{Vector\{String\}}). \\
\bottomrule
\end{tabular}
\medskip

\begin{lstlisting}
julia> p = profile(320193);

julia> p.name, p.entityType, p.sic, p.fiscalYearEnd
("Apple Inc.", "operating", "3571", "0926")
\end{lstlisting}

\subsection{Filings: List, Download, Extract}
\label{sec:api-filings}

\begin{longtable}{@{}p{0.46\textwidth}p{0.50\textwidth}@{}}
\toprule
\textbf{Function} & \textbf{Purpose} \\
\midrule
\endhead
\code{download\_filing(cik, accession; destdir)} & Download a filing's primary
  document into \code{destdir}; tries common URL patterns, saving the first that
  returns HTTP 200. \\
\code{parse\_filing(path)} & Convert a filing's HTML to text (\code{Gumbo} +
  \code{Cascadia}). \\
\code{extract\_section(html, names; max\_chars)} & Pull named sections (e.g.\
  \code{"Item 7"}, \code{"Management's Discussion"}) from filing HTML/text. \\
\code{save\_filing(text, metadata; outdir)} & Write extracted text + metadata to
  disk. \\
\bottomrule
\end{longtable}

\subsubsection{download\_filing}

\sig{download\_filing(cik, accession; destdir = ".")}

\noindent Download a filing's document from the EDGAR \code{Archives} into
\code{destdir} (created if needed) and return the local file path. The accession
number may be given with or without dashes. Several common document/index URL
patterns are tried in turn; the first that responds with HTTP 200 is saved, and
the function throws if none succeed.

\subsubsection{parse\_filing}

\sig{parse\_filing(path)}

\noindent Convert the filing HTML at \code{path} to plain text, using \code{Gumbo}
and \code{Cascadia} to strip markup. The extraction helpers operate on this text.

\subsubsection{extract\_section}

\sig{extract\_section(html, names; max\_chars = 200\_000, base\_path = nothing)}

\noindent Pull named sections from filing HTML/text by heuristic,
case-insensitive matching --- e.g.\ \code{"Item 7"} or
\code{"Management's Discussion"}. Returns a \code{Dict} mapping each requested name
to its extracted text; \code{max\_chars} caps the length kept per section.

\subsubsection{save\_filing}

\sig{save\_filing(text, metadata; outdir = "out")}

\noindent Write extracted \code{text} together with its \code{metadata} to disk
under \code{outdir}, returning the path written.

\begin{lstlisting}
# List a company's recent filings, then download the most recent one
rows = filings_by_cik("0000320193"; forms = "8-K")
for f in first(rows, 5)
    println(f.filed, "  ", f.form, "  ", f.accession)
end

path = download_filing("0000320193", rows[1].accession; destdir = "filings")

# Convert to text and extract named sections
html     = parse_filing(path)
sections = extract_section(html, ["Item 7", "Management's Discussion"])
println(get(sections, "Item 7", "(not found)"))
\end{lstlisting}

\subsection{Financial Data (XBRL)}
\label{sec:api-xbrl}

\begin{longtable}{@{}p{0.46\textwidth}p{0.50\textwidth}@{}}
\toprule
\textbf{Function} & \textbf{Purpose} \\
\midrule
\endhead
\code{company\_facts(cik)} & Every XBRL fact a filer has reported, in one
  (large) document. \\
\code{company\_concept(cik, taxonomy, tag)} & One concept over time for a single
  filer (lighter than \code{company\_facts}). \\
\code{xbrl\_frames(taxonomy, tag, unit, period)} & One concept for one period
  across every filer that reported it (a cross-section). \\
\bottomrule
\end{longtable}

\subsubsection{company\_facts}

\sig{company\_facts(cik)}

\noindent Every XBRL fact a company has ever reported, in a single (often several
megabyte) document from the \code{/api/xbrl/companyfacts/} endpoint, as parsed
JSON. \code{cik} may be an integer or a string, with or without leading zeros.
Facts are grouped by taxonomy under \code{.facts} (e.g.\ \code{:dei},
\code{Symbol("us-gaap")}).

\subsubsection{company\_concept}

\sig{company\_concept(cik, taxonomy, tag)}

\noindent One XBRL concept over time for a single filer, from
\code{/api/xbrl/companyconcept/} --- lighter than \code{company\_facts} when you
want a single line item. Observations live under \code{.units} keyed by unit (e.g.
\code{.units.USD}), each carrying \code{start}/\code{end}, \code{val}, \code{fy},
\code{fp}, \code{form} and \code{filed}.

\subsubsection{xbrl\_frames}

\sig{xbrl\_frames(taxonomy, tag, unit, period)}

\noindent One XBRL concept for one period across \emph{every} filer that reported
it, from \code{/api/xbrl/frames/} --- a cross-section rather than a time series. A
trailing \code{I} on \code{period} denotes an instant (e.g.\ \code{"CY2022Q4I"});
drop it for a duration (e.g.\ \code{"CY2022"}). Rows are under \code{.data}.

\begin{lstlisting}
facts   = company_facts("320193")
concept = company_concept("320193", "us-gaap", "NetIncomeLoss")
frame   = xbrl_frames("us-gaap", "Assets", "USD", "CY2022Q4I")

# Each observation carries: start, end, val, fy/fp, form, filed, accn, frame?
for o in filter(o -> o.form == "10-K", concept.units.USD)
    println(o.fy, "  ", o.val)
end
\end{lstlisting}

\subsection{Credentials and Caching}
\label{sec:caching}

\paragraph{Credentials (the User-Agent).}
There is no API key; the only credential is the SEC \code{User-Agent}
(\S\ref{sec:ua}).

\begin{longtable}{@{}p{0.46\textwidth}p{0.50\textwidth}@{}}
\toprule
\textbf{Function} & \textbf{Purpose} \\
\midrule
\endhead
\code{set\_user\_agent(user\_agent)} & Set the User-Agent from a single
  \code{"name email"} string (validated). \\
\code{get\_user\_agent()} & Return the User-Agent that will be sent (explicit
  value $\to$ \code{SEC\_USER\_AGENT} env var $\to$ error). \\
\code{persist\_user\_agent(user\_agent; depot)} & Validate, set for this session,
  and write \code{SEC\_USER\_AGENT} into the depot's \code{startup.jl} so every
  future session has it. \\
\code{unpersist\_user\_agent(; depot)} & Remove the line that
  \code{persist\_user\_agent} wrote. \\
\bottomrule
\end{longtable}

\subsubsection{set\_user\_agent}

\sig{set\_user\_agent(user\_agent)}

\noindent Set the SEC \code{User-Agent} for the current process from a single
\code{"name email"} string. It is validated (non-empty, contains an email) and
returned. A User-Agent is required before any request; without one EDGAR.jl stops
with a clear error \emph{before} contacting the SEC.

\subsubsection{get\_user\_agent}

\sig{get\_user\_agent()}

\noindent Return the \code{User-Agent} that will be sent, following the resolution
order: an explicit value from \code{set\_user\_agent}/\code{set\_config}, else the
\code{SEC\_USER\_AGENT} environment variable, else an error.

\subsubsection{persist\_user\_agent}

\sig{persist\_user\_agent(user\_agent; depot = first(DEPOT\_PATH))}

\noindent Validate and set the User-Agent for this session, \emph{and} write
\code{SEC\_USER\_AGENT} into the depot's \code{startup.jl} so every future Julia
session has it. \code{depot} selects which Julia depot's startup file to write.

\subsubsection{unpersist\_user\_agent}

\sig{unpersist\_user\_agent(; depot = first(DEPOT\_PATH))}

\noindent Remove the \code{SEC\_USER\_AGENT} line that \code{persist\_user\_agent}
wrote from the depot's \code{startup.jl}. Returns \code{true} if a line was
removed, \code{false} if there was nothing to remove.

\paragraph{Caching.}
Responses are cached so repeated calls in a session do not re-download the same
data. The \code{cache} keyword of \code{set\_config} selects where the cache
lives and how long it survives:

\begin{itemize}[nosep]
  \item \code{:temporary} (default) --- an ephemeral per-process directory,
    deleted when Julia exits. Nothing persists across sessions.
  \item \code{:persistent} --- kept in \code{\textasciitilde/.cache/EDGAR.jl}
    (or \code{XDG\_CACHE\_HOME}) across sessions; files older than
    \code{cache\_max\_age} are pruned automatically.
  \item \code{:off} --- no caching; every call re-fetches.
\end{itemize}

\noindent
Two \textbf{independent} time limits apply: \code{cache\_ttl} (default 24\,h) is
\emph{freshness} --- how long a cached response is reused before being re-fetched
(it deletes nothing); \code{cache\_max\_age} (default 7\,days) is \emph{retention}
--- how long a file is kept on disk before being pruned. \code{cache\_max\_size}
(default 10\,MB) caps the size of any single cached response.

\begin{longtable}{@{}p{0.46\textwidth}p{0.50\textwidth}@{}}
\toprule
\textbf{Function} & \textbf{Purpose} \\
\midrule
\endhead
\code{set\_config(; cache, cache\_dir, cache\_ttl, cache\_max\_size,
  cache\_max\_age, host\_whitelist, allow\_file, user\_agent)} & Override the
  global runtime configuration (only the keywords you pass change). \\
\code{clean\_cache()} & Prune the cache on demand. \\
\code{cache\_metrics()} & Inspect hit/miss/request/byte counters. \\
\code{cache\_path\_for(url)} & The on-disk cache path for a given URL. \\
\bottomrule
\end{longtable}

\subsubsection{set\_config}

\sig{set\_config(; cache, cache\_dir, cache\_ttl, cache\_max\_size, cache\_max\_age, host\_whitelist, allow\_file, user\_agent)}

\noindent Override the global runtime configuration, returning the updated
\code{EDGARConfig}. Only the keywords you pass are changed; the rest keep their
current values. \code{cache} selects the mode (\code{:temporary} / \code{:persistent}
/ \code{:off}); \code{cache\_ttl} sets freshness and \code{cache\_max\_age}
retention; \code{cache\_max\_size} caps a single response; \code{user\_agent} is an
alternative to \code{set\_user\_agent}.

\subsubsection{clean\_cache}

\sig{clean\_cache(max\_age\_seconds = CACHE\_TTL)}

\noindent Prune the on-disk cache on demand, deleting entries older than
\code{max\_age\_seconds} and returning the number removed.

\subsubsection{cache\_metrics}

\sig{cache\_metrics()}

\noindent Return a \code{Dict} of the session's cache counters --- hits, misses,
requests and bytes --- for inspecting cache effectiveness.

\subsubsection{cache\_path\_for}

\sig{cache\_path\_for(url)}

\noindent Return the on-disk cache path EDGAR.jl would use for \code{url}, whether
or not it is currently cached.

\begin{lstlisting}
set_config(cache = :persistent, cache_ttl = 3600)   # keep across sessions, 1h freshness
m = cache_metrics()                                  # (; hits, misses, requests, ...)
clean_cache()
\end{lstlisting}

\subsection{Low-Level Requests}
\label{sec:api-lowlevel}

\subsubsection{fetch\_url}

\sig{fetch\_url(url; use\_cache = true, timeout = 15, allow\_file = false)}

\noindent The primitive every function above is built on: it returns the raw
response body as bytes (or \code{nothing} on failure), with the configured
\code{User-Agent} and the cache applied. Use it as an escape hatch to reach SEC
endpoints EDGAR.jl does not yet wrap, then parse the bytes yourself (e.g.\ with
\code{JSON3.read}).

\begin{lstlisting}
body = fetch_url("https://data.sec.gov/submissions/CIK0000320193.json")
data = JSON3.read(body)
\end{lstlisting}


% ===========================================================================
\subsection{Glossary}
\label{sec:glossary}

SEC filings and their structured (XBRL) data come with their own vocabulary.
The terms that matter here:

\begin{description}[leftmargin=1.4em,style=nextline,itemsep=2pt]
  \item[CIK] \emph{Central Index Key}, the SEC's unique ID for a filer,
    zero-padded to 10 digits (Apple $\to$ \code{0000320193}). Functions accept it
    as an integer or a string, with or without leading zeros (\code{320193}
    $\equiv$ \code{0000320193}). Look one up from a ticker or company name with
    \code{cik}.
  \item[Filing] a document submitted to the SEC, identified by an
    \textbf{accession number} and a \textbf{form type} (\code{10-K} annual
    report, \code{10-Q} quarterly, \code{8-K} current report, \dots). Get a
    filer's filings with \code{filings\_by\_cik}.
  \item[XBRL] \emph{eXtensible Business Reporting Language}, the machine-readable
    format companies tag their financial statements in; it is what makes the
    numbers queryable rather than locked inside a document.
  \item[iXBRL] \emph{Inline XBRL}: those same tags embedded directly inside the
    filing's human-readable HTML, so one document is both readable and
    machine-parseable. The SEC has required it for financial statements since
    around 2019.
  \item[Fact] a single reported number: one \emph{concept}, for one
    \emph{period}, in one \emph{unit} (e.g.\ ``net income for FY2023 was
    96{,}995{,}000{,}000 USD''). \code{company\_facts} returns every fact a
    company has reported.
  \item[Concept] the \emph{name} of a reported line item, drawn from a taxonomy
    (e.g.\ \code{NetIncomeLoss}, \code{Assets}, \code{Revenues}) --- ``what is
    being measured''. \code{company\_concept} returns one concept over time.
  \item[Taxonomy] a dictionary that defines concepts. The big one is
    \textbf{\code{us-gaap}} (US accounting standards); \textbf{\code{dei}}
    (\emph{Document and Entity Information}) holds metadata about the filing
    itself; \textbf{\code{srt}} holds shared elements; \textbf{\code{ifrs-full}}
    is for filers reporting under IFRS; and each company has its own
    \textbf{extension} namespace (e.g.\ \code{aapl} for Apple-specific concepts).
  \item[Frame] a cross-section: one concept, one unit, one period, across
    \emph{every} filer that reported it. \code{xbrl\_frames} returns a frame.
  \item[Unit] the unit of measure of a fact: \code{USD}, \code{shares},
    \code{USD/shares} (per-share), \code{pure} (a ratio), \dots
  \item[Period] the time a fact covers, and how it is written. \textbf{Frames}
    use \emph{calendar} periods: \code{CY} + year, as in \code{CY2022} (a full
    calendar year), \code{CY2022Q4} (a quarter), or \code{CY2022Q4I} (a single
    instant --- note the trailing \code{I}). An \textbf{instant} is a point in
    time (balance-sheet items such as Assets, at quarter-end); a
    \textbf{duration} is a span (income-statement items such as Revenue). By
    contrast, \textbf{\code{FY}} in a company's own facts is its \emph{fiscal}
    year, which need not match the calendar (Apple's \code{FY2023} ended in
    September 2023).
\end{description}
\end{document}
